ODGI: understanding pangenome graphs

### 2021-11-10 manuscript/fig_extract_viz_draw_position_untangle.tex
missing `s`

        \textbf{(e)} \textit{odgi viz} color by path depth: using the Spectra color palette with 4 level of path depths, white indicates no depth, while grey, red, and yellow indicate depth 1, 2, and greater than or equal to 3, respectively.

>>>>

        \textbf{(e)} \textit{odgi viz} color by path depth: using the Spectra color palette with 4 levels of path depths, white indicates no depth, while grey, red, and yellow indicate depth 1, 2, and greater than or equal to 3, respectively.
